\papertitle

### 2014-03-18 final-report/paper.tex
Refactor

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\overview}{Fragment Overview\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

The \overview shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall View}

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overview\xspace}

@@

The \overall shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall}
